Best Practices for Alchemical Free Energy Calculations: v\versionnumber

### 2019-07-16 paper/manuscript.tex
fixing control sequence problems after new contributions.

\begin{figure}
    \includegraphics[width=0.95\linewidth,angle=270]{paper/figures/fig2/Fig2.pdf}
    \caption{{\bf Thermodynamic cycle for computing the relative free energy of binding ($\Delta \Delta G$) between two related small molecules to a supramolecular host.}
    The relative binding free energy difference between two small molecules, $\Delta \Delta G_{\mathrm{bind}, A \rightarrow B} \equiv \Delta G_{\mathrm{bind}, B} - \Delta G_{\mathrm{bind}, A}$---here benzyl alcohol (top) to toluene (bottom)---can be computed as a difference between two alchemical transformations, $\Delta G_\mathrm{bound} - \Delta G_\mathrm{solvated}$, where $\Delta G_\mathrm{bound}$ represents the free energy change of transforming $A \rightarrow B$ in complex and $\Delta G_\mathrm{solvated}$ the free energy change of transforming $A \rigtharrow B$ in solvent.}
    \label{fig:fig1}
\end{figure}
\todo[inline, color=green!20]{This section needs to be expanded and give a good introduction to the theoretical background without going into too much detail.}

@@

\begin{figure}
    \includegraphics[width=0.95\linewidth]{paper/figures/fig3/Fig2_dummy.pdf}
    \caption{a) Bad alignment of congeneric series b) good alignment}
    \label{fig:fig1}
\end{figure}

@@

\subsection*{Free energies of hydration or partition coefficients}
Preliminary considerations necessary for using free energy methods to compute partition coefficients are much generally much more straight forward. Using even something such as bable to generate a 3D minimised structure of the solute you would like to compute a free energy of hydration or partition coefficient can be sufficient for preparation of these types of simulations. However, in these cases a careful choice of forcefields, as well as water models or organic solvents is essential. See for example XX.et al~\cite{xxx} for a good discussion on these choices. 
\todo[inline, color=green!20]{Just a note as a reminder: Chirality!}
%
%
%
%%%%%%%%%%%%
% Step 1   %
%%%%%%%%%%%%
%
\section{What simulation protocol should I choose? -- Step 2}
\label{sec:step2}
Alchemical free energy calculations can be grouped into two main categories, ``absolute'' and ``relative'' \footnote{The distinction is a bit of a misnomer, since both compute ratios of partition functions relative to another state, and neither computes an absolute free energy.}, which differ in whether they compute properties for a single molecule (absolute) or compare properties of different, usually closely related, molecules (relative).
To use binding as a concrete example, in absolute binding free energy calculations, one computes the binding free energy of a ligand to an individual receptor relative to a standard reference concentration.
In contrast, in relative binding free energy calculations, one compares the binding free energy of two related inhibitors to determine the potency difference.
\subsection*{Absolute and relative free energy calculations have some differences}
Many protocol issues for alchemical calculations are common, but some are different between absolute and relative calculations, so before treating the common elements we treat the protocol differences.
\todo[inline, color=greeen!20]{JM: single/dual hybrid toplogies what are they? ASJSM: These have been addressed below}

@@

\begin{figure}
    \includegraphics[width=0.95\linewidth]{paper/figures/fig6/Fig6.pdf}
    \caption{Absolute thermodynamic cycle}
    \label{fig:fig1}
\end{figure}

@@

\begin{itemize}
    \item \textbf{The Zwanzig relationship} Perhaps the simplest method for calculating free energy
differences from simulations is the so-called \textit{Zwanzig
relationship}~\cite{orig.TPT}, also called EXP or simply free energy perturbation, thought that term later grew to encompass all ways of calculating free energy differences.
The free energy between two states defined by two different potential energy functions 
$U_0(\vec{q})$ and $U_1(\vec{q})$ over coordinate space $\vec{q}$ can be calculated as:
\begin{eqnarray}
\Delta f_{01} & = & \ln \expect{e^{-(U_1(\vec{q}) - U_0(\vec{q}))}}_0 =  \ln \expect{e^{-\Delta U(\vec{q})} }_0
\end{eqnarray}\label{eqn.zwanzig}
In words, we take the samples generated during our run with the potential energy function $U_0(\vec{q}}$, recalculate what the energy difference would be to switch to potential energy function $U_1(\vec{q}}$, and exponentially average them to get the free energy.  Here, the exponential average consists in multiplying by -1, exponentiating, averaging, taking the logarithm, and multiplying by -1 again.  This almost requires no extra code functionality to perform; one need only to save a full precision trajectory, and run an unmodified molecular simulation code using the $U_1$ in order to calculate the new energies.  The analysis can be written in a line of code.  We note that this method is even more general, in that the instantaneous work to change the potential energy function from $U_0$ to $U_1$ can be replaced by the nonreversible work $W$ to make the same change some conditions~\cite{???} 
Although the Zwanzig equation is formally correct (as long as the two states considered sample the same phase space volume), it has some very important numerical issues that mean that it is usually when performing a standard free energy calculation for a small molecule.~\cite{shirts.comparison,LuND:Appmcf}  One can show that if the standard deviation of the difference $\Delta U(\vec{q}) = U_1(vec{q})-U_2(\vec{q})$ over all sampled $\vec{q}$ is large (which in this case, means only several times $k_BT)$, then very few samples contribute to the average, and the answer will be both biased and extremely noisy~\cite{???}.  There are a number of applicatitons where it is useful, but those usually involve investigating the dependence of the free energy on small changes in parameters, not changing molecules or even single atoms in molecules~cite{???}

@@

If we have the ensemble of differences in the potential energy both sampled from the distribution defined by $U_0$ and the distribution defined by $U_1$, we can obtain a significantly improved estimate of the
free energy difference compared to that obtained by EXP.  
This estimate was first derived by Bennett and is hence generally called the Bennett Acceptance Ratio.  It is solved by finding the reduced free energy $f_{ij}$ that satisfied the following implicit equation:
\begin{eqnarray}
 \sum_{i=1}^{n_i} \frac{1}{1 + \exp(\ln(n_i/n_j) + u_{ij}(\vec{q}) - f_{ij}))} \\
 =\sum_{i=1}^{n_j} \frac{1}{1 + \exp(\ln(n_j/n_i) - U_{ij}(\vec{q}) + f_ij))} 
\end{eqnarray}
where $n_i$ and $n_j$ are the number of samples from each state. We
will refer to this method as BAR. More recent derivations shows that this formula is the maximum likelihood estimate of the free energy difference
given sets of samples from the two states~\citebold{shirts.bennett}.

Many studies have demonstrated both the
theoretical and practical superiority of BAR over EXP in molecular
simulations~\citebold{shirts.comparison,LuND:Appmcf}, and BAR converges to EXP in the limit that all samples are from a
single state~\citebold{bennettCH,shirts.bennett}. Significantly less
overlap between the configurational space of each state is required to
converge than for EXP, though some overlap must still exist.

The Bennett acceptance ratio is only defined between two states.  Usually, the endpoints of interest in a free energy calculation are sufficiently different that we will need a chain of states that gradually change the potential energy function from $U_0$to $U_1$, as discussed in Section~\ref{sec:???}. One can simply carry out BAR between each pair of states $\Delta G_{1 \rightarrow N} = \Delta_G_{1\rightarrow 2} + \Delta_G_{2\rightarrow 3} +  \ldots + \Delta_G_{N-1\rightarrow N}$.

There is one important thing to note about the uncertainty estimates when summing multiple free energies together to calculate an overall free energy estimate.  Although BAR itself gives a free energy estimate that is asymptotically correct in and is much less biased than the uncertainty estimate for EXP, the uncertainties in $\Delta_G_{i-1\rightarrow i}$ and $\Delta_G_{i\rightarrow i+1}$ are not uncorrelated, because they both involve the energies $U_i(\vec{q})$. The variances of each of the free energies will \textit{not} sum to the variance of the overall free energy. Instead, some other uncertainty method such as bootstrapping~\cite{???} must be used.

\item \textit{Thermodynamic integration} 
By taking the derivative of the free energy with respect to the
variable $\lambda$, we find that:
\begin{equation}
df/d\lambda &=& \frac{d}{d\lambda} \ln \int e^{-u(\lambda,\vec{q})} d\vec{q} = \expect{\frac{du(\lambda,\vec{q})}{d\lambda}\
}_{\lambda} 
\end{equation}

And than we can then numerically integrate $df/d\lambda$ over an alchemical transformation, using a range of different well-established techniques, to obtain:
\begin{equation}
\Delta f    &=& \int_{0}^{1} \expect{\frac{du(\lambda,\vec{q})}{d\lambda}}_{\lambda}  d\lambda    
\end{equation}
This approach to calculating the free energy is called thermodynamic integration (TI). Averaging over $\expect{\frac{du}{d\lambda}}$ requires
fewer uncorrelated samples to reach a given level of relative error
than averaging $e^{-u(\vec{q})}$, as the range is usually
narrower with a more Gaussian distribution. Rather than being limited by overlap, as in the case of BAR and MBAR, we are instead limited by the bias in the numerical quadrature, which must be minimized sufficiently to be beneath the level of statistical noise.

Various numerical integration schemes are possible, but the trapezoid
rule provides a simple and robust scheme.  All types of
numerical integration can be written as:
\[ \Delta f \approx \sum_{k=1}^{K} w_k
\expect{\frac{du(\lambda,\vec{q})}{d\lambda}}_{k} \] where the weights
$w_k$ correspond to a particular choice of numerical integration.
Researchers have tried a large number of different integration
schemes~\citebold{resat.mezei.93,jorge_effect_2010,shyu_reducing_2009}. For However, many other integration choices require specific choices of $\lambda$
to minimize bias, which makes them unsuitable when the intermediates
have widely-varying levels of uncertainty. For example, integrating a cubic spline interpolation provided negligble benefits~\cit{paliwal.benchmark}. For starting researchers, we therefore recommend a simple trapezoid rule scheme, as it allows for maximal flexibility in which values of $\lambda$ are simulated.  Because fitting to higher
order polynomials can have numerical instabilities for some energy functions, and because alternate functional forms might only be appropriate
with some types of transformations, expertise and experience is
required to perform such numerical integration modifications.  In practice, adding 2-3 more intermediates is sufficient to match the performance of these more complicated numerical quadrature schemes.

@@

\item \textit{MBAR}. One can generalize Bennett's logic from two states to multiple states to obtain a free energy estimator that uses energy differences along.  MBAR gives a system of implicit equations for the free energies $f_i$:
\begin{eqnarray}
f_i = \sum_{n=1}^{N} \frac{\exp(-u_i(\vec{q}_n}{\sum_{k=1}^K N_k \exp(f_k-u_k(\vec{q}_n}))}
\end{eqnarray}
where there are $N_k$ samples from each of $K$ states, with $N=\sum_k N_k$ the total number of samples. Thus, we need to evaluate the energy function $U_i$ for all samples obtained at all states in the transformation. The equations can be solved by a number of different standard routines.  We note that there are only $K-1$ independent equations, so one of the $f_i$ must be specified.

@@

\item BAR is essentially just as good as MBAR for highly optimized $\lambda$ intermediates.  Specifically, if the $\lambdas$ are chosen such that intermediate states have moderate overlap with their neighbors (i.e. between $i$ and $i+1$ and between $i$ and $i-1$, they will \testit{not} have significant overlap with their next nearest neighbors $i+2$ and $i-2$. Thus MBAR doesn't actually get significant information from these energy differences, so one might as well not even calculate them, and just perform BAR between nearest neighbors.~\cite{paliwal.benchmark} 

@@

\begin{itemize}
\item Examining output data for common problems with discussions of what exactly to plot or look at; examples of typical curves for dV/dlambda and free energy versus lambda, for example
\begin{itemize}
\item Make sure ligand doesn’t tumble out of binding site (Mey has observed this)
\item Significant discrepancies between different free energy estimators (TI, BAR, MBAR)
\item Poor replica mixing (for replica-exchange)
\item Correlation time as a function of lambda as it would be expected to be a smooth
\item Dependence on initial conformation
\item Torsional analysis: Is it stuck in specific states? Only very rarely transitions?
\item More “usual suspects”
\end{itemize}
\end{itemize}
\item Other considerations for many transformations
\todo[inline]{JM: add references, maybe a diagram ?}
Cycle closure error
Additional analyses may be performed when free energy changes for multiple transformations are available and the desired free energy difference between two molecules A and B may be obtained through more than one pathway connecting. This usually applies to relative free energy calculations. 
For instance the free energy change for the transformation of molecule A into molecule B should be the opposite of the free energy change for the transformation of molecule B into molecule A. Significant deviations from this may indicate insufficient configurational sampling along the lambda schedule of one or both transformations. The approach may be generalised to sets of connected transformations given the requirement that the sum of free energy changes along edges of a closed network should be zero. In practice this is not observed and deviations become increasingly large as the size of the cycle increases owing to propagation of statistical errors. Though no firm guidelines have emerged, it may be judicious to perform additional configurational sampling along edges of a network that are involved in cycles closing poorly. This may be done by extending simulations duration, or by averaging free energy changes over multiple repeats. The later approach may yield more reproducible free energy changes, but at the expense of a stronger bias on the estimated free energies due to repeated use of the same input coordinates. 
A scheme to reduce cycle closure errors is used in FEP+ whereby calculated free energy changes along the nodes of the network are re-sampled assuming estimates of the calculated free energy change along a node may be obtained from a Gaussian distribution centered on the estimated free energy change and with a standard deviation equal to the estimated standard deviation of the free energy change. The procedure then uses a Maximum likelihood method to find new sets of free energy changes that minimize cycle closure errors (REF). An alternative approach computes the free energy change between a target and reference compound as a weighted average over all unique paths in the network, with the weights derived from the propagated uncertainties of each node (REF).

>>>>

\begin{figure}
    \includegraphics[width=0.95\linewidth,angle=270]{paper/figures/fig2/Fig2.pdf}
    \caption{{\bf Thermodynamic cycle for computing the relative free energy of binding ($\Delta \Delta G$) between two related small molecules to a supramolecular host.}
    The relative binding free energy difference between two small molecules, $\Delta \Delta G_{\mathrm{bind}, A \rightarrow B} \equiv \Delta G_{\mathrm{bind}, B} - \Delta G_{\mathrm{bind}, A}$---here benzyl alcohol (top) to toluene (bottom)---can be computed as a difference between two alchemical transformations, $\Delta G_\mathrm{bound} - \Delta G_\mathrm{solvated}$, where $\Delta G_\mathrm{bound}$ represents the free energy change of transforming $A \rightarrow B$ in complex and $\Delta G_\mathrm{solvated}$ the free energy change of transforming $A \rightarrow B$ in solvent.}
    \label{fig:fig1}
\end{figure}
\todo[inline, color=green!20]{This section needs to be expanded and give a good introduction to the theoretical background without going into too much detail.}

@@

\begin{figure}
    \includegraphics[width=0.95\linewidth]{paper/figures/fig2/Fig2.pdf}
    \caption{a) Bad alignment of congeneric series b) good alignment}
    \label{fig:fig1}
\end{figure}

@@

\subsection*{Free energies of hydration or partition coefficients}
Preliminary considerations necessary for using free energy methods to compute partition coefficients are much generally much more straight forward. Using even something such as bable to generate a 3D minimised structure of the solute you would like to compute a free energy of hydration or partition coefficient can be sufficient for preparation of these types of simulations. However, in these cases a careful choice of forcefields, as well as water models or organic solvents is essential. See for example XX.et al~\cite{xxx} for a good discussion on these choices. 
\todo[inline, color=green!20]{Just a note as a reminder: Chirality!}
%
%
%
%%%%%%%%%%%%
% Step 1   %
%%%%%%%%%%%%
%
\section{What simulation protocol should I choose? -- Step 2}
\label{sec:step2}
Alchemical free energy calculations can be grouped into two main categories, ``absolute'' and ``relative'' \footnote{The distinction is a bit of a misnomer, since both compute ratios of partition functions relative to another state, and neither computes an absolute free energy.}, which differ in whether they compute properties for a single molecule (absolute) or compare properties of different, usually closely related, molecules (relative).
To use binding as a concrete example, in absolute binding free energy calculations, one computes the binding free energy of a ligand to an individual receptor relative to a standard reference concentration.
In contrast, in relative binding free energy calculations, one compares the binding free energy of two related inhibitors to determine the potency difference.
\subsection*{Absolute and relative free energy calculations have some differences}
Many protocol issues for alchemical calculations are common, but some are different between absolute and relative calculations, so before treating the common elements we treat the protocol differences.
\todo[inline, color=green!20]{JM: single/dual hybrid toplogies what are they? ASJSM: These have been addressed below}

@@

\begin{figure}
    \includegraphics[width=0.95\linewidth]{paper/figures/fig6/Fig3.pdf}
    \caption{Absolute thermodynamic cycle}
    \label{fig:fig1}
\end{figure}

@@

\begin{itemize}
    \item \textbf{The Zwanzig relationship} Perhaps the simplest method for calculating free energy
differences from simulations is the so-called \textit{Zwanzig
relationship}~\cite{orig.TPT}, also called EXP or simply free energy perturbation, thought that term later grew to encompass all ways of calculating free energy differences.
The free energy between two states defined by two different potential energy functions 
$U_0(\vec{q})$ and $U_1(\vec{q})$ over coordinate space $\vec{q}$ can be calculated as:
\begin{eqnarray}
\Delta f_{01} & = & \ln \expect{e^{-(U_1(\vec{q}) - U_0(\vec{q}))}}_0 =  \ln \expect{e^{-\Delta U(\vec{q})} }_0
\end{eqnarray}\label{eqn.zwanzig}
In words, we take the samples generated during our run with the potential energy function $U_0(\vec{q})$, recalculate what the energy difference would be to switch to potential energy function $U_1(\vec{q})$, and exponentially average them to get the free energy.  Here, the exponential average consists in multiplying by -1, exponentiating, averaging, taking the logarithm, and multiplying by -1 again.  This almost requires no extra code functionality to perform; one need only to save a full precision trajectory, and run an unmodified molecular simulation code using the $U_1$ in order to calculate the new energies.  The analysis can be written in a line of code.  We note that this method is even more general, in that the instantaneous work to change the potential energy function from $U_0$ to $U_1$ can be replaced by the non-reversible work $W$ to make the same change some conditions~\cite{xx} 
Although the Zwanzig equation is formally correct (as long as the two states considered sample the same phase space volume), it has some very important numerical issues that mean that it is usually when performing a standard free energy calculation for a small molecule.~\cite{shirts.comparison,LuND:Appmcf}  One can show that if the standard deviation of the difference $\Delta U(\vec{q}) = U_1(vec{q})-U_2(\vec{q})$ over all sampled $\vec{q}$ is large (which in this case, means only several times $k_BT)$, then very few samples contribute to the average, and the answer will be both biased and extremely noisy~\cite{xx}.  There are a number of applications where it is useful, but those usually involve investigating the dependence of the free energy on small changes in parameters, not changing molecules or even single atoms in molecules~\cite{xx}

@@

If we have the ensemble of differences in the potential energy both sampled from the distribution defined by $U_0$ and the distribution defined by $U_1$, we can obtain a significantly improved estimate of the
free energy difference compared to that obtained by EXP.  
This estimate was first derived by Bennett and is hence generally called the Bennett Acceptance Ratio.  It is solved by finding the reduced free energy $f_{ij}$ that satisfied the following implicit equation:
\begin{eqnarray}
 \sum_{i=1}^{n_i} \frac{1}{1 + \exp(\ln(n_i/n_j) + u_{ij}(\vec{q}) - f_{ij}))} \\
 =\sum_{i=1}^{n_j} \frac{1}{1 + \exp(\ln(n_j/n_i) - U_{ij}(\vec{q}) + f_ij))} 
\end{eqnarray}
where $n_i$ and $n_j$ are the number of samples from each state. We
will refer to this method as BAR. More recent derivations shows that this formula is the maximum likelihood estimate of the free energy difference
given sets of samples from the two states~\cite{shirts.bennett}.

Many studies have demonstrated both the
theoretical and practical superiority of BAR over EXP in molecular
simulations~\cite{shirts.comparison,LuND:Appmcf}, and BAR converges to EXP in the limit that all samples are from a
single state~\cite{bennettCH,shirts.bennett}. Significantly less
overlap between the configurational space of each state is required to
converge than for EXP, though some overlap must still exist.

The Bennett acceptance ratio is only defined between two states.  Usually, the endpoints of interest in a free energy calculation are sufficiently different that we will need a chain of states that gradually change the potential energy function from $U_0$to $U_1$, as discussed in Section~\ref{}. One can simply carry out BAR between each pair of states $\Delta G_{1 \rightarrow N} = \Delta {G_{1\rightarrow 2}} + \Delta {G_{2\rightarrow 3}} +  \ldots + \Delta G_{N-1\rightarrow N}$.

There is one important thing to note about the uncertainty estimates when summing multiple free energies together to calculate an overall free energy estimate.  Although BAR itself gives a free energy estimate that is asymptotically correct in and is much less biased than the uncertainty estimate for EXP, the uncertainties in $\Delta {G_{i-1\rightarrow i}}$ and $\Delta {G_{i\rightarrow i+1}}$ are not uncorrelated, because they both involve the energies $U_i(\vec{q})$. The variances of each of the free energies will \textit{not} sum to the variance of the overall free energy. Instead, some other uncertainty method such as bootstrapping~\cite{???} must be used.

\item \textit{Thermodynamic integration} 
By taking the derivative of the free energy with respect to the
variable $\lambda$, we find that:
\begin{equation}
df/d\lambda = \frac{d}{d\lambda} \ln \int \exp{-u(\lambda,\vec{q})} d\vec{q} = \expect{\frac{du(\lambda,\vec{q})}{d\lambda}\
}_{\lambda} 
\end{equation}

And than we can then numerically integrate $df/d\lambda$ over an alchemical transformation, using a range of different well-established techniques, to obtain:
\begin{equation}
\Delta f    = \int_{0}^{1} \expect{\frac{du(\lambda,\vec{q})}{d\lambda}}_{\lambda}  d\lambda    
\end{equation}
This approach to calculating the free energy is called thermodynamic integration (TI). Averaging over $\expect{\frac{du}{d\lambda}}$ requires
fewer uncorrelated samples to reach a given level of relative error
than averaging $e^{-u(\vec{q})}$, as the range is usually
narrower with a more Gaussian distribution. Rather than being limited by overlap, as in the case of BAR and MBAR, we are instead limited by the bias in the numerical quadrature, which must be minimized sufficiently to be beneath the level of statistical noise.

Various numerical integration schemes are possible, but the trapezoid
rule provides a simple and robust scheme.  All types of
numerical integration can be written as:
\[ \Delta f \approx \sum_{k=1}^{K} w_k
\expect{\frac{du(\lambda,\vec{q})}{d\lambda}}_{k} \] where the weights
$w_k$ correspond to a particular choice of numerical integration.
Researchers have tried a large number of different integration
schemes~\cite{resat.mezei.93,jorge_effect_2010,shyu_reducing_2009}. For However, many other integration choices require specific choices of $\lambda$
to minimize bias, which makes them unsuitable when the intermediates
have widely-varying levels of uncertainty. For example, integrating a cubic spline interpolation provided negligble benefits~\cite{paliwal.benchmark}. For starting researchers, we therefore recommend a simple trapezoid rule scheme, as it allows for maximal flexibility in which values of $\lambda$ are simulated.  Because fitting to higher
order polynomials can have numerical instabilities for some energy functions, and because alternate functional forms might only be appropriate
with some types of transformations, expertise and experience is
required to perform such numerical integration modifications.  In practice, adding 2-3 more intermediates is sufficient to match the performance of these more complicated numerical quadrature schemes.

@@

\item \textit{MBAR}. One can generalize Bennett's logic from two states to multiple states to obtain a free energy estimator that uses energy differences along.  MBAR gives a system of implicit equations for the free energies $f_i$:
\begin{equation}
f_i = \sum_{n=1}^{N} \frac{\exp(-u_i(\vec{q}_n}{\sum_{k=1}^K N_k \exp(f_k-u_k(\vec{q}_n}))
\end{equation}
where there are $N_k$ samples from each of $K$ states, with $N=\sum_k N_k$ the total number of samples. Thus, we need to evaluate the energy function $U_i$ for all samples obtained at all states in the transformation. The equations can be solved by a number of different standard routines.  We note that there are only $K-1$ independent equations, so one of the $f_i$ must be specified.

@@

\item BAR is essentially just as good as MBAR for highly optimized $\lambda$ intermediates.  Specifically, if the $\lambda$s are chosen such that intermediate states have moderate overlap with their neighbors (i.e. between $i$ and $i+1$ and between $i$ and $i-1$, they will \testit{not} have significant overlap with their next nearest neighbors $i+2$ and $i-2$. Thus MBAR doesn't actually get significant information from these energy differences, so one might as well not even calculate them, and just perform BAR between nearest neighbors.~\cite{paliwal.benchmark} 

@@

\subsubsection{Are my simulations any good?}
\todo[inline, color={green!20}]{ASJSM: write and tidy}

\todo[inline, color={yellow!20}]{@MKuhn: write section on overlap with example plots}
\begin{itemize}
\item Examining output data for common problems with discussions of what exactly to plot or look at; examples of typical curves for dV/dlambda and free energy versus lambda, for example
\begin{itemize}
\item Make sure ligand doesn’t tumble out of binding site (Mey has observed this)
\item Significant discrepancies between different free energy estimators (TI, BAR, MBAR)
\item Poor replica mixing (for replica-exchange)
\item Correlation time as a function of lambda as it would be expected to be a smooth
\item Dependence on initial conformation
\item Torsional analysis: Is it stuck in specific states? Only very rarely transitions?
\item More “usual suspects”
\end{itemize}
\item Other considerations for many transformations
\end{itemize}

\todo[inline]{JM: add references, maybe a diagram ?}
Cycle closure error
Additional analyses may be performed when free energy changes for multiple transformations are available and the desired free energy difference between two molecules A and B may be obtained through more than one pathway connecting. This usually applies to relative free energy calculations. 
For instance the free energy change for the transformation of molecule A into molecule B should be the opposite of the free energy change for the transformation of molecule B into molecule A. Significant deviations from this may indicate insufficient configurational sampling along the lambda schedule of one or both transformations. The approach may be generalised to sets of connected transformations given the requirement that the sum of free energy changes along edges of a closed network should be zero. In practice this is not observed and deviations become increasingly large as the size of the cycle increases owing to propagation of statistical errors. Though no firm guidelines have emerged, it may be judicious to perform additional configurational sampling along edges of a network that are involved in cycles closing poorly. This may be done by extending simulations duration, or by averaging free energy changes over multiple repeats. The later approach may yield more reproducible free energy changes, but at the expense of a stronger bias on the estimated free energies due to repeated use of the same input coordinates. 
A scheme to reduce cycle closure errors is used in FEP+ whereby calculated free energy changes along the nodes of the network are re-sampled assuming estimates of the calculated free energy change along a node may be obtained from a Gaussian distribution centered on the estimated free energy change and with a standard deviation equal to the estimated standard deviation of the free energy change. The procedure then uses a Maximum likelihood method to find new sets of free energy changes that minimize cycle closure errors (REF). An alternative approach computes the free energy change between a target and reference compound as a weighted average over all unique paths in the network, with the weights derived from the propagated uncertainties of each node (REF).
